### 2019-03-30 stableLimit.tex
change stableLimit.tex

%!TEX spellcheck
%%%----Versions-----------------------------
%stable-limit6.tex 2018/6/27 by Zhenyao-----
%stable-limit5.tex 2018/6/22 by Renming------
%stable-limit4.tex 2018/6/21 by Yanxia-------
%stable-limit3.tex 2018/6/13 by Zhenyao-------
%---The preamble----------------------
\documentclass[12pt, a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
\usepackage{hyperref}
%new added
\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
%end new added
\usepackage{mathrsfs}
\usepackage{mathtools}
%new added
\mathtoolsset{showonlyrefs}
%end new added
\usepackage{stackrel}
%Deleted
%\usepackage{autonum}
%\usepackage{amsmath}
%end Deleted 
%ZY: \mathtoolsset{showonlyrefs} commond can do the trick of 'autonum' package.
%ZY: amsmath package is included in the amsart document class
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cro}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
%\newtheorem{innerasp}{Assumption}
%\newenvironment{asp}[1]{\renewcommand\theinnerasp{#1}\innerasp}{\endinnerasp}
\numberwithin{equation}{section}
\allowdisplaybreaks
%---Top matter------------------------------
\begin{document}
\title
	%[Manuscript]
	[Superprocesses with stable branching]
	{\large Limit theorems for a class of critical superprocesses with stable branching}
	%\author{Yan-Xia Ren, Renming Song and Zhenyao Sun}
	\author[Y.-X. Ren, R. Song and Z. Sun]{Yan-Xia Ren, Renming Song and Zhenyao Sun}
%---Yan-Xia Ren
\address
	{Yan-Xia Ren\\
	School of Mathematical Sciences\\
	Peking University\\
	Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
%---Renming Song
\address
	{Renming Song\\
	Dept of Mathematics\\
	University of Illinois at Urbana-Champaign\\
	Urbana, IL 61801}
\email{rsong@illinois.edu}
\thanks{The research of Renming Song is supported in part by the Simons Foundation (\#429343, Renming Song).}
%---Zhenyao Sun
\address
	{Zhenyao Sun\\
	School of Mathematical Sciences\\
	Peking University\\
	Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\begin{abstract}
	In this paper, we consider a critical $(\xi,\psi)$-superprocess 
%	$\{(X_t)_{t\geq 0}; (\mathbf P_\mu)_{\mu \in \mathcal M^1_E}\}$.
$\{X; \mathbf P_\mu\}$.
	$\xi$, the spatial motion of the superprocess, is a 
%	Hunt process on a locally compact separable metric space $E$, 
Hunt process, on a locally compact separable metric space $E$, 
	satisfying an intrinsically ultracontractive condition.
	$\psi$, the branching mechanism of the superprocess, is a function on $E \times [0,\infty]$ of the form
\begin{equation}
	\psi(x,z)
	= -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\end{equation}
%	where $\beta \in \mathscr B_b(E),$ $\gamma \in \mathscr B^+_b(E)$ and $\kappa \in \mathscr B^+_b(E)$ satisfy 
with $\beta \in \mathscr B_b(E),$ $\gamma \in \mathscr B^+_b(E)$ and $\kappa \in \mathscr B^+_b(E)$ satisfying
\begin{equation}
	1 
	< \gamma(\cdot )
	<2; 
	\quad \gamma_0 
	:= \operatorname{ess\,inf}_{m(dx)} \gamma(x)
	> 1; 
	\quad \operatorname{ess\,inf}_{m(dx)}\kappa(x) 
	> 0.
\end{equation}

	We show that $\mathbf P_{\delta_x}( \| X_t \| \neq 0) $ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $(\gamma_0 - 1)^{-1}$.
	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, we show that 
\begin{equation}
	\mathbf P_{\delta_x}( \|X_t\| \neq0) 
	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t,
\end{equation} 
	and for a large class of non-negative testing functions $f$,  
\begin{equation}
	\{\eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | \|X_t\|\neq 0) \} 
	\xrightarrow[t\to \infty]{\operatorname{law}} \langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
\end{equation} 
	where $\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform
\begin{equation}
	E[e^{- u \mathbf z^{(\alpha)}}]
	= 1 - (1+ u^{-\alpha})^{-1/\alpha},
	\quad u \geq 0.
\end{equation}
\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}
%\date{}
\maketitle
\section{Introduction}

\subsection{Background}
	The study of the asymptotic behaviors of critical branching particle systems has a long history.
	It is well known that for a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$, we have
\begin{equation}\label{eq: Kolmogorov's result with finite variance}
	n P(Z_n > 0)
	\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2}
\end{equation}
	and
\begin{equation}\label{eq: Yaglom's result with finite variance}
	\Big\{ \frac{Z_n}{n}; P(\cdot| Z_n > 0) \Big\}
	\xrightarrow[n \to \infty]{\operatorname{law}} \frac{\sigma^2}{2} \mathbf e,
\end{equation}
	where $\sigma^2$ is the variance of the offspring distribution and $\mathbf e$ is an exponential random variable with mean $1$.
	The result \eqref{eq: Kolmogorov's result with finite variance} is due to Kolmogorov \cite{Kolmogorov1938Zur-losung}, and the result \eqref{eq: Yaglom's result with finite variance} is due to Yaglom \cite{Yaglom1947Certain}.
	For further references to these results, see \cite{Harris2002The-theory} and \cite{KestenNeySpitzer1966The-Galton-Watson}.
%	Since then, lots of analogous results were obtained for more general 
	Since then, lots of analogous results have been obtained for more general
	critical branching processes with finite 2nd moment, see \cite{AsmussenHering1983Branching}, \cite{AthreyaNey1974Functionals}, \cite{AthreyaNey1972Branching} and \cite{JoffeSpitzer1967On-multitype} for example.

	Notice that \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if  $\sigma^2 = \infty$,  see \cite{KestenNeySpitzer1966The-Galton-Watson} for example.
    In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, and thus more appropriate scalings are needed.
	Research in this direction was first conducted by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up, which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance. 
	The main result of  \cite{Slack1968A-branching} can be stated as follows. Consider a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$
	with infinite variance.
	Assume that the  generating function $f(s)$ of the offspring distribution is of the form
\begin{equation}\label{eq: offspring generating function with alpha moment}
	f(s)
	= s + (1-s)^{1+ \alpha} l(1-s),
	\quad s\geq 0,
\end{equation}
	where $\alpha\in (0, 1]$ and $l$ is a function slowly varying at $0$.
	Then
\begin{equation} \label{eq: extinction probability of critical GW process without 2rd moment}
	P(Z_n > 0) 
	= n^{-1/\alpha} L(n),
\end{equation}
	where $L$ is a function slowly varying at $\infty$, and
\begin{equation} \label{eq: conditional distribution of critical GW process without 2rd moment}
	\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}
	\xrightarrow[n\to \infty]{\operatorname{law}} \mathbf z^{(\alpha)},
\end{equation}
	where $\mathbf z^{(\alpha)}$ is a positive random variable with Laplace transform
\begin{equation}
	E[e^{- u \mathbf z^{(\alpha)}}]
	= 1 - (1+ u^{-\alpha})^{-1/\alpha},
	\quad u \geq 0.
\end{equation}
	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ \emph{Zolotarev's distribution with index $\alpha$}.
	Slack \cite{Slack1972Further} also considered the converse of this problem:
	In order for $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have
	a non-degenerate weak limit, 
    the generating function of the offspring distribution must be of  
	the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
	For shorter and more unified approaches to these results, we refer our readers to Borovkov \cite{Borovkov1989Method} and Pakes \cite{Pakes2010Critical}.

	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment 
    condition. Their main result can be stated as follows. 
	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
	Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the generating function of the offspring distribution, and by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ be its left and right  eigenvectors, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
	Suppose that
\begin{equation}\label{eq: regularly varying condition for multitype branching process}
	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
	= x^\alpha l(x),
	\quad x > 0,
\end{equation}
	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$; 
	and the matrix $G(\mathbf s)$ is defined by
\begin{equation}
	\mathbf 1 - \mathbf F(\mathbf s)
	= (M - G(\mathbf s))(\mathbf 1 - \mathbf s),
	\quad \mathbf s \in \mathbb R_+^d.
\end{equation}
    Let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
	It was shown in \cite{GoldsteinHoppe1978Critical} that, for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\begin{equation} \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
	n L(a_n) \operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
	\xrightarrow[n\to \infty]{} 
	\frac{(\mathbf i \cdot \mathbf u)^\alpha}\alpha,
\end{equation}
	and for each $\mathbf j \in \mathbb N_0^d$,
\begin{equation}\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)},
\end{equation}
	where $\mathbf z^{(\alpha)}$ is a random variable with  Zolotarev's distribution with index  $\alpha$.
	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} to have a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
	Vatutin \cite{Vatutin1977Limit} also considered analogous results for the continuous time multitype critical Galton-Watson processes.

%	Asmussen and Hering \cite[Section~6.3~and~6.4]{AsmussenHering1983Branching} 
	Asmussen and Hering \cite[Sections~6.3~and~6.4]{AsmussenHering1983Branching} 
	discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$.
	When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in 
%\cite[Theorem~4.2]{AsmussenHering1983Branching} 
\cite[Theorem~6.4.2]{AsmussenHering1983Branching} 
for critical branching Markov processes.

@@

	It is natural to ask whether results parallel to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} are still valid for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
	A simpler version of this question has already been answered in the context of continuous-state branching processes
	(CSBPs)
	which can be viewed as superprocesses without spatial movements.
	Kyprianou \cite{Kyprianou2008Continuous} considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$. 
	He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
\begin{equation} \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)},
\end{equation}
    where $\mathbf z^{(\gamma - 1)}$ is a random variable with Zolotarev's distribution with index $\gamma - 1$.
	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied
	CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
\begin{equation}\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z)
	= c z^\gamma l(z),
%	\quad z\geq 0.
	\quad z\geq 0,
\end{equation}
	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a function slowly varying  at $0$.
	It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\begin{equation}\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\end{equation}
	Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem: 
%	Suppose that $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP 
Suppose  $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP 
	with critical branching mechanism $\psi$ satisfying Grey's condition.
	In order for the left side of \eqref{eq: conditional limit of CSBP} to have a non-trivial weak limit for some positive constants $(\lambda_t)_{t\geq 0}$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.

>>>>

%!TEX spellcheck
%%%----Versions-----------------------------
%stable-limit7.tex 2018/6/29 by Renming-----
%stable-limit6.tex 2018/6/27 by Zhenyao-----
%stable-limit5.tex 2018/6/22 by Renming------
%stable-limit4.tex 2018/6/21 by Yanxia-------
%stable-limit3.tex 2018/6/13 by Zhenyao-------
%---The preamble----------------------
\documentclass[12pt, a4paper]{amsart}
\setlength{\textwidth}{\paperwidth}\addtolength{\textwidth}{-2in}\calclayout
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{mathrsfs}
\usepackage{mathtools}
\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cro}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{exa}[thm]{Example}
\newtheorem{asp}{Assumption}
\numberwithin{equation}{section}
\allowdisplaybreaks
%---Top matter------------------------------
\begin{document}
\title
	%[Manuscript]
	[Superprocesses with stable branching]
	{\large Limit theorems for a class of critical superprocesses with stable branching}
		\author[Y.-X. Ren, R. Song and Z. Sun]{Yan-Xia Ren, Renming Song and Zhenyao Sun}
%---Yan-Xia Ren
\address
	{Yan-Xia Ren\\
	School of Mathematical Sciences\\
	Peking University\\
	Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
%---Renming Song
\address
	{Renming Song\\
	Dept of Mathematics\\
	University of Illinois at Urbana-Champaign\\
	Urbana, IL 61801}
\email{rsong@illinois.edu}
\thanks{The research of Renming Song is supported in part by the Simons Foundation (\#429343, Renming Song).}
%---Zhenyao Sun
\address
	{Zhenyao Sun\\
	School of Mathematical Sciences\\
	Peking University\\
	Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\begin{abstract}
	In this paper, we consider a critical $(\xi,\psi)$-superprocess
$\{X; \mathbf P_\mu\}$.
	$\xi$, the spatial motion of the superprocess, is a
%Hunt process, on a locally compact separable metric space $E$,
%	satisfying an intrinsically ultracontractive condition.
Hunt process on a locally compact separable metric space $E$ with reference measure $m$.
	$\psi$, the branching mechanism of the superprocess, is a function on $E \times [0,\infty]$ of the form
\begin{equation}
	\psi(x,z)
	= -\beta (x) z + \kappa(x) z^{\gamma(x)},
	\quad x\in E, z \geq 0,
\end{equation}
  with $\beta \in \mathscr B_b(E),$ $\gamma \in \mathscr B^+_b(E)$ and $\kappa \in \mathscr B^+_b(E)$ satisfying
\begin{equation}
	1
	< \gamma(\cdot )
	<2;
	\quad \gamma_0
	:= \operatorname{ess\,inf}_{m(dx)} \gamma(x)
	> 1;
	\quad \operatorname{ess\,inf}_{m(dx)}\kappa(x)
	> 0.
\end{equation}

%	We show that 
	We show that, under some conditions, 
	$\mathbf P_{\delta_x}( \| X_t \| \neq 0) $ converges to $0$ as $t\to \infty$ and is regularly varying at infinity with index $(\gamma_0 - 1)^{-1}$.
	Furthermore, if $m(x: \gamma(x) = \gamma_0)>0$, 
%	we show that
 we show that, for any finite initial measure $\mu$ on $E$, 
\begin{equation}
%	\mathbf P_{\delta_x}( \|X_t\| \neq0)
%	\stackrel[t\to \infty]{}{\sim} \phi(x) \eta_t,
\mathbf P_{\mu}( \|X_t\| \neq0)
	\stackrel[t\to \infty]{}{\sim} \langle\phi \eta_t,
\end{equation}
	and for a large class of non-negative testing functions $f$,
\begin{equation}
	\{\eta_t X_t(f) ; \mathbf P_{\delta_x}(\cdot | \|X_t\|\neq 0) \}
	\xrightarrow[t\to \infty]{\operatorname{law}} \langle f, \phi^*\rangle_m \mathbf z^{(\gamma_0 - 1)},
\end{equation}
%	where 
 where $\phi$ ($\phi^*$, resp.) is the principal eigenfunction of the mean semigroup 
 (the dual of of the eman semigroup) of the superprocess, 	
	$\eta_t := \big( C_X(\gamma_0 - 1) t \big)^{- \frac {1} {\gamma_0 - 1} },$ $C_X := \langle \mathbf 1_{\gamma(\cdot) = \gamma_0} \kappa \phi^{\gamma_0}, \phi^* \rangle_m$ and $\mathbf z^{(\gamma_0 - 1)}$ is a random variable with Laplace transform
\begin{equation}
	E[e^{- u \mathbf z^{(\alpha)}}]
	= 1 - (1+ u^{-\alpha})^{-1/\alpha},
	\quad u \geq 0.
\end{equation}
\end{abstract}
%\subjclass[2010]{60J80, 60F05}
\subjclass[2010]{Premary: 60J68; 60F05. Secondary 60J80; 60J25}
\keywords{Critical superprocess; stable branching, scaling limit; intrinsic ultracontractivity; regular variation}
%\date{}
\maketitle
\section{Introduction}

\subsection{Background}
	The study of the asymptotic behaviors of critical branching particle systems has a long history.
	It is well known that for a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$, we have
\begin{equation}\label{eq: Kolmogorov's result with finite variance}
	n P(Z_n > 0)
	\xrightarrow[n\to \infty]{} \frac{2}{\sigma^2}
\end{equation}
	and
\begin{equation}\label{eq: Yaglom's result with finite variance}
	\Big\{ \frac{Z_n}{n}; P(\cdot| Z_n > 0) \Big\}
	\xrightarrow[n \to \infty]{\operatorname{law}} \frac{\sigma^2}{2} \mathbf e,
\end{equation}
	where $\sigma^2$ is the variance of the offspring distribution and $\mathbf e$ is an exponential random variable with mean $1$.
	The result \eqref{eq: Kolmogorov's result with finite variance} is due to Kolmogorov \cite{Kolmogorov1938Zur-losung}, and the result \eqref{eq: Yaglom's result with finite variance} is due to Yaglom \cite{Yaglom1947Certain}.
	For further references to these results, see \cite{Harris2002The-theory} and \cite{KestenNeySpitzer1966The-Galton-Watson}.
	Since then, lots of analogous results have been obtained for more general
	critical branching processes with finite 2nd moment, see \cite{AsmussenHering1983Branching}, \cite{AthreyaNey1974Functionals}, \cite{AthreyaNey1972Branching} and \cite{JoffeSpitzer1967On-multitype} for example.

	Notice that \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are still valid even if  $\sigma^2 = \infty$,  see \cite{KestenNeySpitzer1966The-Galton-Watson} for example.
    In this case, the limits in \eqref{eq: Kolmogorov's result with finite variance} and \eqref{eq: Yaglom's result with finite variance} are degenerate, and thus more appropriate scalings are needed.
	Research in this direction was first conducted by Zolotarev \cite{Zolotarev1957More} in a simplified continuous time set-up, which is then extended by Slack \cite{Slack1968A-branching} to discrete time critical Galton-Watson processes allowing infinite variance.
	The main result of  \cite{Slack1968A-branching} can be stated as follows. Consider a critical Galton-Watson process $\{(Z_n)_{n\geq 0}; P\}$
	with infinite variance.
	Assume that the  generating function $f(s)$ of the offspring distribution is of the form
\begin{equation}\label{eq: offspring generating function with alpha moment}
	f(s)
	= s + (1-s)^{1+ \alpha} l(1-s),
	\quad s\geq 0,
\end{equation}
	where $\alpha\in (0, 1]$ and $l$ is a function slowly varying at $0$.
	Then
\begin{equation} \label{eq: extinction probability of critical GW process without 2rd moment}
	P(Z_n > 0)
	= n^{-1/\alpha} L(n),
\end{equation}
	where $L$ is a function slowly varying at $\infty$, and
\begin{equation} \label{eq: conditional distribution of critical GW process without 2rd moment}
	\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}
	\xrightarrow[n\to \infty]{\operatorname{law}} \mathbf z^{(\alpha)},
\end{equation}
	where $\mathbf z^{(\alpha)}$ is a positive random variable with Laplace transform
%\begin{equation}
\begin{equation}\label{e:zloltarev}
	E[e^{- u \mathbf z^{(\alpha)}}]
	= 1 - (1+ u^{-\alpha})^{-1/\alpha},
	\quad u \geq 0.
\end{equation}
%	In this paper, we will call the distribution of $\mathbf z^{(\alpha)}$ \emph{Zolotarev's distribution with index $\alpha$}.
	Slack \cite{Slack1972Further} also considered the converse of this problem:
	In order for $\big\{ P(Z_n > 0) Z_n; P(\cdot | Z_n > 0)\big\}$ to have
	a non-degenerate weak limit,
    the generating function of the offspring distribution must be of
	the form of \eqref{eq: offspring generating function with alpha moment} for some $0 < \alpha \leq 1$.
	For shorter and more unified approaches to these results, we refer our readers to Borovkov \cite{Borovkov1989Method} and Pakes \cite{Pakes2010Critical}.

	Goldstein and Hoppe \cite{GoldsteinHoppe1978Critical} considered the asymptotic behavior of multitype critical Galton-Watson processes without the 2nd moment
    condition. Their main result can be stated as follows.
	Let $\mathbf Z_n=(Z_n^{(1)}, \dots, Z_n^{(d)})$ be a critical, $d$-type, nonsingular and positively regular Galton-Watson process.
	Denote by $\mathbf F(\mathbf s) = (\mathbf F_1(\mathbf s), \dots, \mathbf F_d(\mathbf s))$ the generating function of the offspring distribution, and by $\mathbf F^{(n)}(\mathbf s), ~ n>1,$ its $n$th iterates.
	Let $M$ be the mean matrix of $\mathbf Z$, $\mathbf v$ and $\mathbf u$ be its left and right  eigenvectors, respectively, corresponding to the maximal eigenvalue 1, and normalized so that $\mathbf v \cdot \mathbf u = 1$ and $\mathbf 1 \cdot \mathbf u = 1$, with $\mathbf 1$ being the vector $(1,\dots, 1)$.
	Suppose that
\begin{equation}\label{eq: regularly varying condition for multitype branching process}
	\mathbf v G(\mathbf 1-x\mathbf u) \mathbf u
	= x^\alpha l(x),
	\quad x > 0,
\end{equation}
	where $0 < \alpha \leq 1$; $l$ is slowly varying at $0$;
	and the matrix $G(\mathbf s)$ is defined by
\begin{equation}
	\mathbf 1 - \mathbf F(\mathbf s)
	= (M - G(\mathbf s))(\mathbf 1 - \mathbf s),
	\quad \mathbf s \in \mathbb R_+^d.
\end{equation}
    Let $a_n := \mathbf v \cdot (\mathbf 1 - \mathbf F^{(n)}(\mathbf 0))$, with $\mathbf 0 \in \mathbb R_+^d$ being the vector $(0,\dots, 0)$.
	It was shown in \cite{GoldsteinHoppe1978Critical} that, for each $\mathbf i \in \mathbb N_0^d \setminus \{\mathbf 0\}$,
\begin{equation} \label{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes}
	n L(a_n) \operatorname{P}(\mathbf Z_n \neq \mathbf 0| Z_0 = \mathbf i)^\alpha
	\xrightarrow[n\to \infty]{}
	\frac{(\mathbf i \cdot \mathbf u)^\alpha}\alpha,
\end{equation}
	and for each $\mathbf j \in \mathbb N_0^d$,
\begin{equation}\label{eq: conditioned normalized multitype branching process}
	\{ a_n \mathbf Z_n \cdot \mathbf j ; P(\cdot | \mathbf Z_n \neq \mathbf 0, \mathbf Z_0 = \mathbf i)\}
	\xrightarrow[n\to \infty]{\operatorname{law}} (\mathbf v\cdot \mathbf j) \mathbf z^{(\alpha)},
\end{equation}
	where $\mathbf z^{(\alpha)}$ is a random variable with  
%	Zolotarev's distribution with index  $\alpha$.
   Laplace transform given by \eqref{e:zloltarev}.
	For the converse of this problem, Vatutin \cite{Vatutin1977Limit} showed that in order for the left side of \eqref{eq: conditioned normalized multitype branching process} to have a non-degenerate weak limit, one must have \eqref{eq: regularly varying condition for multitype branching process} for some $0 < \alpha \leq 1$.
	Vatutin \cite{Vatutin1977Limit} also considered analogous results for the continuous time multitype critical Galton-Watson processes.

	Asmussen and Hering \cite[Sections~6.3~and~6.4]{AsmussenHering1983Branching}
	discussed similar questions for critical branching Markov processes $(Y_t)$ in a general space $E$ under some ergodicity condition (the so-called condition (M), see \cite[p.~156]{AsmussenHering1983Branching}) on the mean semigroup of $(Y_t)$.
	When the second moment is infinite, under a condition  parallel  to \eqref{eq: regularly varying condition for multitype branching process} (the so-called condition (S) \cite[p.~207]{AsmussenHering1983Branching}), results parallel to \eqref{eq: limit behavior of the exitinction probability without finite variance of multitype branching processes} and \eqref{eq: conditioned normalized multitype branching process} were proved in
\cite[Theorem~6.4.2]{AsmussenHering1983Branching}
for critical branching Markov processes.

@@

	It is natural to ask whether results parallel to \eqref{eq: extinction probability of critical GW process without 2rd moment} and \eqref{eq: conditional distribution of critical GW process without 2rd moment} are still valid for some critical superprocesses without the second moment condition \eqref{eq: second moment condition}.
	A simpler version of this question has already been answered in the context of continuous-state branching processes
	(CSBPs)
	which can be viewed as superprocesses without spatial movements.
	Kyprianou \cite{Kyprianou2008Continuous} considered CSBPs $\{(Y_t)_{t\geq 0}; P\}$ with stable branching mechanism $\psi(z) =c z^\gamma$ where $c > 0$ and $\gamma \in (1,2]$.
	He showed that for all $x\geq 0$, with $c_t := (c(\gamma - 1)t)^{1/(\gamma - 1)}$,
\begin{equation} \label{eq: conditional limit of CSBP with stable branching}
	\{c_t^{-1}Y_t; P( \cdot |Y_t > 0,Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)},
\end{equation}
    where $\mathbf z^{(\gamma - 1)}$ is a random variable with 
%    Zolotarev's distribution with index $\gamma - 1$.
     Laplace transform given by \eqref{e:zloltarev} (with $\alpha=\gamma-1$).
	Recently, Ren, Yang and Zhao \cite{RenYangZhao2014Conditional} studied
	CSBPs $\{(Y_t)_{t\ge 0}; P\}$ with branching mechanism
\begin{equation}\label{eq: regular varing of branching mechanism of a CSBP}
	\psi(z)
	= c z^\gamma l(z),
	\quad z\geq 0,
\end{equation}
	where $c > 0$, $\gamma \in (1,2]$ and $l$ is a function slowly varying  at $0$.
	It was proved in  \cite{RenYangZhao2014Conditional} that for all $x\geq 0$, with $\lambda_t: = P_1(Y_t > 0)$,
\begin{equation}\label{eq: conditional limit of CSBP}
	\{ \lambda_t Y_t ; P(\cdot | Y_t > 0, Y_0 = x)\}
	\xrightarrow[t\to \infty]{\operatorname{law}} \mathbf z^{(\gamma - 1)}.
\end{equation}
	Later, Iyer, Leger and Pego \cite{IyerLegerPego2015Limit} considered the converse problem:
    Suppose  $\{(Y_t)_{t\geq 0}; P\}$ is a CSBP
	with critical branching mechanism $\psi$ satisfying Grey's condition.
	In order for the left side of \eqref{eq: conditional limit of CSBP} to have a non-trivial weak limit for some positive constants $(\lambda_t)_{t\geq 0}$, one must have \eqref{eq: regular varing of branching mechanism of a CSBP} for some $1< \gamma \leq 2$.
